---
title: "Theory of Change for Landscape Water Use"
author: "Jeremy Knox"
date: "4/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Practicum 2: Measurement Strategy
Sketch out a measurement strategy to be paired with a theory of change. You may use the theory of change you wrote up for the previous practicum or you may choose any other documented theory of change from an organization of your choice. Your measurement strategy should focus on the results that are most important in the theory of change and/or the outputs, outcomes, and assumptions that are most uncertain.

## Measure Definition
For purposes of planning, you can assume that your budget for measurement is ~5% of the program cost that you choose. You will want to make sure that your measurement strategy satisfies the goals that we have discussed in the course and that are covered in the relevant readings:
    a. Valid
    b. Proximate
    c. Precise 
    d. Sensitive
    e. Economical 
    f. Practical
    g. Reliable
    h. Interpretable
    i. Useful
    j. Generalizable (if goal is to compare outcomes across programs)
    
You should sketch out the eight most important measures given the theory of change and results framework. Each of these measures should have the following information (see Session 5, USAID 2019 for examples):
    1. Measurement goal
    2. Exact measure to be taken (definition, survey item wording, etc.) 
    3. Unit of measurement
    4. Source of data
    5. Rationale for choice of measure
    6. Responsibility for data collection (who?)
    7. Frequency of data collection


1) “Have you had a rain shut-off sensor installed at your home?” Yes/No/Don’t Know
2) “Have you had a water% adjust sensor installed at your home?” Yes/No/Don’t Know
3) “How much water did your home use in X month vs X month?” (Something like that?” Or water bill?
4) Are you aware of the up to $1,000 rebate for water efficient equipment? 
5) How familiar are you with the Smart Landscape Rebate program? Never heard of it, Not very familiar, somewhat familiar, very familiar?
6) Are you aware of the rebates for water saving landscape sensors? 
7) Do you think your landscape water usage is below average/average/above average/don’t know?
8) Have you added, or plan to add, any of the following to your landscaping in the past X period of time? Native plants (list some examples), Water-wise plants (list some examples), Mulch, Permeable surfaces (artificial grass, gravel, flagstone)


    
## Sampling Strategy
For three of your eight measures, formally declare your sampling strategy in code. The declaration should include:
    1. Description of the target population (in words)
    2. Declaration of hypothetical population (in code)
    3. Description of any challenges to drawing a representative sample (in words) 
    4. Declaration of reporting probabilities (in code)
    5. Description of sampling procedure (in words)
    6. Declaration of sampling procedure (in code)

```{r Jeremy}
# Question: Do you know about the Smart Landscape Rebate program?
# Answer: Yes/No or 1/0
# Sampling Strategy 
# Target population: homeowners and home renters within the city of Santa Barbara 
# Representitive Sample Challenges: Main road bias by spatial location 
# Example: Gibraltar Rd residents are 1/2 as likely to respond to surveys so we will sample them 2x as much to get a representative sample of SB city residents. That means Gibrlatar residents will respond to 10% of the surveys handed out and SB "main" residents will respond to 20% of surveys. Gibrlatar resdents only account for 30% of the population. The population is around 40,000. We intened to sample 250 residents. 

# Load Packages
library(DeclareDesign)
library(knitr)
library(ggplot2)
library(grid)
library(gridExtra)
library(dplyr)
library(kableExtra)

# Declaration of hypothetical population and reporting probabilities
set.seed(777)
population <- declare_population(
  main = add_level(N=2, 
                   baseline=c(.2,.1)),
  homeowner = add_level(N=c(40000*.7, 40000*.3), 
                      know=draw_binary(baseline))
)
pop <- population()
pop.vector <- c(40000*.7, 40000*.3)
my_estimand <- declare_estimands(mean(know), label = "Ybar")
reporting <- declare_assignment(blocks=main,
                  assignment_variable = "R",
                  block_prob=c(0.2,0.1)) #anticipate only 10% of Gibraltar residents and 20% of everyone else to respond to survey
sampling <- declare_sampling(strata=main, 
                             strata_n=c(150,350)) # sampling twice as many 

strata_weighted_mean <- function(data){ 
  data.frame(
    estimator_label = "strata_w_mean", 
    estimand_label = "Ybar",
    n = nrow(data), 
    stringsAsFactors = FALSE,
    estimate = data %>% 
      filter(R==1) %>%
      group_by(main) %>%
      summarise(mean=mean(know)) %>% 
      mutate(prop=pop.vector/sum(pop.vector)) %>% 
      mutate(sub.mean=mean*prop) %>% 
      pull(sub.mean) %>% 
      sum())
}

answer <- declare_estimator(
  handler = tidy_estimator(strata_weighted_mean), 
  estimand = my_estimand)

design <- population + my_estimand + reporting + sampling + answer

diagnosis <- diagnose_design(design, sims = 1000)

diagnosis$diagnosands_df[,c(4,5,12,14)] %>% kable()


```

```{r}

# Load Packages

library(DeclareDesign)
library(knitr)
library(ggplot2)
library(grid)
library(gridExtra)
library(dplyr)
library(kableExtra)

```

### Have you added, or plan to add, any of the following to your landscaping in the past X period of time?

Responses:
- Native plants (list some examples)
- Water-wise plants (list some examples)
- Mulch
- Permeable surfaces (artificial grass, gravel, flagstone)
- None of the above
- Don’t know

```{r}

# Set population of SB based on # of households in SB City, according to US Census data (rounded up to 40,000 for simplicity's sake). Probability is based on data from https://bit.ly/2zSrEdT, which reports a 40% homeownership rate.
# Probability: estimating that 70% of homeowners control their landscaping decisions, while only 30% of renters control their landscaping decisions.

set.seed(228)
population <- declare_population(
  households = add_level(N=40000, 
     homeowner=draw_binary(N=N, prob = 0.4),
     plan_to_plant=correlate(given = homeowner, rho = 0.5,
                         draw_binary, prob = 0.5)
))

pop <- population()

kable(table(pop$homeowner,pop$plan_to_plant)) %>% 
  add_header_above(c("homeowner"=1,"plan_to_plant"=2))

# Generate estimand
my_estimand <- declare_estimands(mean(plan_to_plant),
                                 label = "Ybar")
```

## DeclareDesign()

```{r declare-report}

# Block probabilities represent how likely it is that a survey respondent actually is in control of their landscaping. If they're not in control of their landscaping, they are not likley to even respond to the survey. 
rent_or_own <- declare_assignment(blocks=homeowner,
                  assignment_variable = "P",
                  block_prob=c(0.3,0.7))

# We want to get a good idea of whether our program influenced people to make changes in the garden, so we want to hear more from people who are more likely to have control over their own gardens. We oversample homeowners to bias the average response towards people who are more likely to be in control of their landscaping, and therefore more likely to respond or make water-wise changes in the garden. 
sampling <- declare_sampling(strata=homeowner,
                             strata_n=c(150,350))
```

## DeclareDesign()

```{r declare-estimator}

strata_weighted_mean <- function(data){
  data.frame(  
  estimator_label = "strata_w_mean",
  estimand_label = "Ybar",
  n = nrow(data),
  stringsAsFactors = FALSE,
  
  estimate = data %>% filter(P==1) %>%
    group_by(homeowner) %>% 
    summarise(mean=mean(plan_to_plant)) %>%
    mutate(prop=c(0.3,0.7)) %>%
    mutate(sub.mean=mean*prop) %>% pull(sub.mean) %>% 
    sum())
}

```

## DeclareDesign()

```{r diagnosis, cache=TRUE}

answer <- declare_estimator(
  handler = tidy_estimator(strata_weighted_mean),
  estimand = my_estimand)

design <- population + my_estimand + rent_or_own +
          sampling + answer

diagnosis <- diagnose_design(design, sims = 1000)

diagnosis$diagnosands_df[,c(4,5,12,14)] %>%
  kable()

```